Program Optimisations via Hylomorphisms for Extraction of Executable Code

### 2025-07-07 paper/paper.tex
Preparing cameraready sources
identity and associativity

\subsection{Elements of Category Theory}
A \emph{category} is a collection of objects $A, B, C$, denoted by $\Obj(\CatC)$
and a collection of arrows $f, g, h$ between these objects, denoted by $\Arr
(\CatC)$, such that there always exists an identity arrow $id_{A} : A \to A$ for
each object $A$ and for two arrows $A \xrightarrow{f} B$ and $B \xrightarrow{g}
C$ there always exists an arrow $A \xrightarrow{g\circ f} C$ obeying the
associativity law. We denote $\Hom_{\CatC} (A, B)$ the set of arrows from $A$ to
$B$ and we use the letters $\CatC$, $\CatD$, $\CatE\dots$ for
categories\footnote[1]{For presentation purposes we shall not deal with size
  issues and assume all the categories are locally small.}. The initial object (when it exists), denoted by $0$,
is the object such that for any other object $A$
there is a unique arrow $0 \xrightarrow{!} A$.  Dually, the terminal object (when it exists),
denoted by $1$, is the object such that for any other object $A$ there is a
unique arrow $A \xrightarrow{!} 1$. As a result of the uniqueness properties, initial and terminal objects are unique up-to
isomorphism.

>>>>

\subsection{Elements of Category Theory}
A \emph{category} is a collection of objects $A, B, C$, denoted by $\Obj(\CatC)$
and a collection of arrows $f, g, h$ between these objects, denoted by $\Arr
(\CatC)$, such that there always exists an identity arrow $id_{A} : A \to A$ for
each object $A$ and for two arrows $A \xrightarrow{f} B$ and $B \xrightarrow{g}
C$ there always exists an arrow $A \xrightarrow{g\circ f} C$ obeying the identity and
associativity law. We denote $\Hom_{\CatC} (A, B)$ the set of arrows from $A$ to
$B$ and we use the letters $\CatC$, $\CatD$, $\CatE\dots$ for
categories\footnote[1]{For presentation purposes we shall not deal with size
  issues and assume all the categories are locally small.}. The initial object (when it exists), denoted by $0$,
is the object such that for any other object $A$
there is a unique arrow $0 \xrightarrow{!} A$.  Dually, the terminal object (when it exists),
denoted by $1$, is the object such that for any other object $A$ there is a
unique arrow $A \xrightarrow{!} 1$. As a result of the uniqueness properties, initial and terminal objects are unique up-to
isomorphism.
